Errata

### 2025-04-08 tex/Results_Discussion.tex
Add titles to figures and tables

\begin{sidewaysfigure}
    \centering
    % The \includegraphics command remains the same
    \includegraphics[width=1\textwidth]{img/baseline_by_site.png}
    % The caption remains the same
    \caption{Soil physical and chemical properties across the four study sites (PdA: Pan de Azúcar, SG: Santa Gracia, LC: La Campana, and NA: Nahuelbuta). Letter-based display accompanying soil properties with significant effect for site. Different letters indicate statistically significant differences ($p < 0.05$, Šidák correction).}
    % The label remains the same
    \label{fig:baseline_site}
\end{sidewaysfigure}

@@

% I will include it sideways for better visualization
\begin{sidewaysfigure}
    \centering
    % The \includegraphics command remains the same
    \includegraphics[width=1\textwidth]{img/baseline_by_biocrust_interaction.png}
    % The caption remains the same, clean up the p<0.05 part
    \caption{Biocrust (a) and interaction (b) effects on soil properties. Soil physical and chemical properties across for biocrust (BSC+ vs. BSC-) and the interaction with the site (PdA: Pan de Azúcar, SG: Santa Gracia, LC: La Campana, and NA: Nahuelbuta). Letter-based display accompanying soil properties with significant effect for site or site*biocrust. Different letters indicate statistically significant differences ($p < 0.05$, Šidák correction).} % Use math mode for p < 0.05
    % The label remains the same
    \label{fig:baseline_biocrust_interaction}
\end{sidewaysfigure} % *** End sidewaysfigure environment ***

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/aggregate stability indexes_se.png}
	\caption{Aggregate stability indexes for Pan de Azúcar (PdA), Santa Gracia (SG), La Campana (LC), and Nahuelbuta (NA) for biocrust (BSC+) and non-biocrust (BSC-) treatments displayes as mean and standard error. $\Delta$MWD: difference in mean weight diameter, $\Delta$GMD: difference in geometric mean diameter, WSAR: water stability aggregate ratio, R$_{<\SI{2}{\milli\meter}}$: ratio of aggregates less than \SI{2}{\milli\meter}.}
	\label{fig:aggregate-stability}
\end{figure}
\FloatBarrier

@@

\begin{sidewaystable} % Using sidewaystable instead of table
    % \centering % Centering is often implicit/less relevant for full-page sideways tables
    \begin{threeparttable}
        \caption{Surface runoff fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. Different letters indicate statistically significant different values based on Šidák correction post-hoc test results.}
        \label{tab:runoff_fluxes}

@@

\begin{sidewaystable} % Using sidewaystable for landscape orientation
    \begin{threeparttable}
        \caption{Percolating water fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. Different letters indicate statistically significant different values based on Šidák correction post-hoc test results.}
        \label{tab:percolation_fluxes} % Unique label for this table

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/nutrient-flow-diagram.png}
	\caption{Representation of total carbon in sediments and DOC in water fluxes for the four study sites. The diagrams at the right side with slightly green surface represents the BSC+ treatments and the one at the left the BSC-. Grey-filled arrows correspond to C fluxes, and yellowish arrows to N. At the same time, arrows with solid borders correspond to the flow attached to the sediments, and dashed arrows dissolved in water. Each type of arrow is proportional inside each group in width to the concentration of nutrients and in length to the mass of it.}
	\label{fig:nutrient-flow}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/PCA-microbes-structure.jpg}
	\caption{Principal Component Analyses of soil properties in native soils (squares) and sterilized soils (circles) including significant soil properties. A) arid, B) semi-arid, C) mediterranean and D) humid site. Microbial influence is indicated by sample separation along the x-axis.}
	\label{fig:PCA-microbes}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/bacterial-abundance.png}
	\caption{Relative abundance of top 15 bacterial phyla for Pan de Azúcar and Santa Gracia and the different time points. Time is represented as T0 (original), T1 (2 weeks), T2 (12 weeks) and T3 (16 weeks). Each bubble is the mean of the different treatments (in situ, BSCs and plants) and technical triplicates.}
	\label{fig:bacterial-abundance}
\end{figure}

>>>>

\begin{sidewaysfigure}
    \centering
    % The \includegraphics command remains the same
    \includegraphics[width=1\textwidth]{img/baseline_by_site.png}
    % The caption remains the same
    \caption[Soil physical and chemical properties across the four study sites]{Soil physical and chemical properties across the four study sites (PdA: Pan de Azúcar, SG: Santa Gracia, LC: La Campana, and NA: Nahuelbuta). Letter-based display accompanying soil properties with significant effect for site. Different letters indicate statistically significant differences ($p < 0.05$, Šidák correction).}
    % The label remains the same
    \label{fig:baseline_site}
\end{sidewaysfigure}

@@

% I will include it sideways for better visualization
\begin{sidewaysfigure}
    \centering
    % The \includegraphics command remains the same
    \includegraphics[width=1\textwidth]{img/baseline_by_biocrust_interaction.png}
    % The caption remains the same, clean up the p<0.05 part
    \caption[Soil physical and chemical properties for the biocrust and interaction effects]{Biocrust (a) and interaction (b) effects on soil properties. Soil physical and chemical properties across for biocrust (BSC+ vs. BSC-) and the interaction with the site (PdA: Pan de Azúcar, SG: Santa Gracia, LC: La Campana, and NA: Nahuelbuta). Letter-based display accompanying soil properties with significant effect for site or site*biocrust. Different letters indicate statistically significant differences ($p < 0.05$, Šidák correction).} % Use math mode for p < 0.05
    % The label remains the same
    \label{fig:baseline_biocrust_interaction}
\end{sidewaysfigure} % *** End sidewaysfigure environment ***

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/aggregate stability indexes_se.png}
	\caption[Aggregate stability indexes on the study sites]{Aggregate stability indexes for Pan de Azúcar (PdA), Santa Gracia (SG), La Campana (LC), and Nahuelbuta (NA) for biocrust (BSC+) and non-biocrust (BSC-) treatments displayes as mean and standard error. $\Delta$MWD: difference in mean weight diameter, $\Delta$GMD: difference in geometric mean diameter, WSAR: water stability aggregate ratio, R$_{<\SI{2}{\milli\meter}}$: ratio of aggregates less than \SI{2}{\milli\meter}.}
	\label{fig:aggregate-stability}
\end{figure}
\FloatBarrier

@@

\begin{sidewaystable} % Using sidewaystable instead of table
    % \centering % Centering is often implicit/less relevant for full-page sideways tables
    \begin{threeparttable}
        \caption[Surface runoff fluxes on the study sites]{Surface runoff fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. Different letters indicate statistically significant different values based on Šidák correction post-hoc test results.}
        \label{tab:runoff_fluxes}

@@

\begin{sidewaystable} % Using sidewaystable for landscape orientation
    \begin{threeparttable}
        \caption[Percolating water fluxes on the study sites]{Percolating water fluxes on the study sites (SG: Santa Gracia, QdT: Quebrada de Talca, LC: La Campana, NA: Nahuelbuta) with (+) and without (-) biocrust (BSC) cover. Values correspond to mean $\pm$ standard deviation (SD) of five field replicates. Different letters indicate statistically significant different values based on Šidák correction post-hoc test results.}
        \label{tab:percolation_fluxes} % Unique label for this table

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/nutrient-flow-diagram.png}
	\caption[Conceptual diagram of total carbon (C) and nitrogen (N) fluxes in sediment and water for the four study sites]{Representation of total carbon (C) and nitrogen (N) fluxes in sediment and water for the four study sites. Diagonal arrows represent surface runoff. Arrows pointing vertically downward represent percolation. The diagrams on the right, with a light green surface, represent the BSC+ treatments, and the one on the left represents the BSC- treatments. Grey-filled arrows correspond to C fluxes, and yellowish arrows to N. At the same time, arrows with solid borders correspond to fluxes attached to the sediments and dashed arrows correspond to fluxes dissolved in water. Each type of arrow is proportional within each group in width to the concentration of nutrients and in length to their mass.}
	\label{fig:nutrient-flow}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/PCA-microbes-structure.jpg}
	\caption[Principal Component Analyses of soil properties in native and sterilized soils including significant soil properties]{Principal Component Analyses of soil properties in native soils (squares) and sterilized soils (circles) including significant soil properties. A) arid, B) semi-arid, C) mediterranean and D) humid site. Microbial influence is indicated by sample separation along the x-axis.}
	\label{fig:PCA-microbes}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=1\textwidth]{img/bacterial-abundance.png}
	\caption[Relative abundance of top 15 bacterial phyla for Pan de Azúcar and Santa Gracia and the different time points]{Relative abundance of top 15 bacterial phyla for Pan de Azúcar and Santa Gracia and the different time points. Time is represented as T0 (original), T1 (2 weeks), T2 (12 weeks) and T3 (16 weeks). Each bubble is the mean of the different treatments (in situ, BSCs and plants) and technical triplicates.}
	\label{fig:bacterial-abundance}
\end{figure}
